\chapter*{}
\thispagestyle{empty}
\addtocounter{page}{-1}

\renewcommand\bibname{List of publications}

\begin{thebibliography}{CDG07}

\bibitem[CDG07]{Chira07Stigmergic}
C.~Chira, D.~Dumitrescu, and \textbf{R.~D. G\u{a}ceanu}.
\newblock Stigmergic agent systems for solving {NP}-hard problems.
\newblock {\em Studia Informatica}, Special Issue KEPT-2007: Knowledge
  Engineering: Principles and Techniques (June 2007):177--184, June 2007.
\newblock \textbf{(indexed MathSciNet, Zentralblatt MATH, EBSCO Publishing).}

  

\bibitem[GP10]{Gaceanu10AnAdaptive}
\textbf{R.~D. G{\u{a}}ceanu} and H.~F. Pop.
\newblock An adaptive fuzzy agent clustering algorithm for search engines.
\newblock In {\em MACS2010: Proceedings of the 8th Joint Conference on
  Mathematics and Computer Science}, pages 185--196. Komarno, Slovakia, 2010.
\newblock \textbf{(indexed MathematicalReviews).}

\bibitem[GP11a]{Gaceanu11AContext}
\textbf{R.~D. G{\u{a}}ceanu} and H.~F. Pop.
\newblock A context-aware {ASM}-based clustering algorithm.
\newblock {\em Studia Universitatis Babes-Bolyai Series Informatica},
  LVI(2):55--61, 2011.
\newblock \textbf{(indexed MathSciNet, Zentralblatt MATH, EBSCO Publishing).}
  
  \bibitem[GO11]{Gaceanu11Using}
\textbf{R.~D. G{\u{a}}ceanu} and G.~Orb{\'{a}}n.
\newblock Using rsl to describe the stock exchange domain.
\newblock In {\em microCAD International Scientific Conference}. University of
  Miskolc, Hungary, 31 March -- 1 April 2011.
\newblock \textbf{(International conference).}

\bibitem[GP11b]{Gaceanu11AFuzzy}
\textbf{R.~D. G{\u{a}}ceanu} and H.~F. Pop.
\newblock A fuzzy clustering algorithm for dynamic environments.
\newblock In {\em KEPT2011: Knowledge Engineering Principles and Techniques,
  Selected Papers, Eds: M. Frentiu, H.F. Pop, S. Motogna}, pages 119--130.
  Babes-Bolyai University, Cluj-Napoca, Romania, July 4--6 2011.
\newblock \textbf{(ISI --- Conference Proceedings Citation Index).}

\bibitem[GP11c]{Gaceanu11AnIncremental}
\textbf{R.~D. G{\u{a}}ceanu} and H.~F. Pop.
\newblock An incremental {ASM}-based fuzzy clustering algorithm.
\newblock In {\em Informatics'2011, Slovakia, i'11:Proceedings of the Eleventh
  International Conference on Informatics, Informatics 2011, Eds: V.
  Novitzk{\'{a}}, {\u{S}}tefan Hud{\'{a}}k}, pages 198--204. Slovak Society for
  Applied Cybernetics and Informatics, Ro{\u{z}}{\u{n}}ava, Slovakia, November
  16--18 2011.  
\newblock \textbf{(indexed MathematicalReviews).}
  
  \bibitem[G{\u{a}}c11]{Gaceanu11ABio}
\textbf{Radu~D. G{\u{a}}ceanu}.
\newblock A bio-inspired fuzzy agent clustering algorithm for search engines.
\newblock {\em Procedia Computer Science}, 7(0):305 -- 307, 2011.
\newblock Proceedings of the 2nd European Future Technologies Conference and
  Exhibition 2011 (FET 11),
\newblock 10.1016/j.procs.2011.09.060.
\newblock http://www.sciencedirect.com/science/article/pii/S187705091100620X.  
\newblock \textbf{(ISI --- Conference Proceedings Citation Index).}
  
\bibitem[CCGa]{Czibula11Intelligent}
Gabriela Czibula, Istvan Czibula, and \textbf{Radu~D. G{\u{a}}ceanu}.
\newblock Intelligent data structures selection using neural networks.
\newblock {\em Knowledge and Information Systems}, Springer London, pages 1--22.
\newblock 10.1007/s10115-011-0468-3.  
\newblock \textbf{(ISI --- Science Citation Index Expanded) \color{red} IF = 2.0} \color{black} (2010)

\bibitem[GP12]{Gaceanu12SCP}
\textbf{R.~D. G{\u{a}}ceanu} and H.~F. Pop.
\newblock An incremental approach to the set covering problem.
\newblock {\em Studia Universitatis Babes-Bolyai Series Informatica}, LVIII(2),
  2012. --- under review.
\newblock \textbf{(indexed MathSciNet, Zentralblatt MATH, EBSCO Publishing).}

\bibitem[CCGb]{Czibula12SVM}
Gabriela Czibula, Istvan Czibula, and \textbf{Radu~D. G{\u{a}}ceanu}.
\newblock A Support Vector Machine Model For Intelligent Selection of Data Representations.
\newblock {\em Applied Soft Computing} --- under review.
\newblock \textbf{(ISI --- Science Citation Index Expanded) \color{red} IF = 2.1} \color{black} (2010)



  
  
\end{thebibliography}

\begin{comment}

\begin{itemize}

\item C. Chira, D. Dumitrescu, \textbf{R. D. G\u{a}ceanu}, Stigmergic Agent Systems for Solving NP-hard Problems, KEPT2007: Knowledge Engineering Principles and Techniques, June 6--8 2007, pp. 177--184, Cluj-Napoca, Romania.
\item \textbf{R. D.  G\u{a}ceanu}, H. F. Pop, An Adaptive Fuzzy Agent Clustering Algorithm for Search Engines, MACS2010: Proceedings of the 8th Joint Conference on Mathematics and Computer Science, 2010, Kom\'{a}rno, Slovakia.
\item \textbf{R. D. G\u{a}ceanu}, G. Orb\'{a}n, Using RSL to Describe the Stock Exchange Domain, microCAD International Scientific Conference University of Miskolc, Hungary, 31 March -- 1 April 2011, Miskolc, Hungary.
\item \textbf{R. D.  G\u{a}ceanu}, H. F. Pop, A context-aware ASM-based clustering algorithm, Studia Universitatis Babes-Bolyai Series Informatica, LVI(2): 55--61, 2011.
\item  \textbf{R. D. G\u{a}ceanu}, A Bio-Inspired Fuzzy Agent Clustering Algorithm for Serach Engines, 
Procedia Computer Science, 7(0):305 – 307. Proceedings of the 2nd
European Future Technologies Conference and Exhibition 2011 (FET 11), 
10.1016/j.procs.2011.09.060, \\
http://www.sciencedirect.com/science/article/pii/S187705091100620X.
\item  \textbf{R.D. G\u{a}ceanu}, H.F. Pop, A Fuzzy Clustering Algorithm for Dynamic Environments, KEPT2011: Knowledge Engineering Principles and Techniques, Selected Papers, Eds: M. Frentiu, H.F. Pop, S. Motogna, July 4--6 2011, pp. 119--130, Cluj-Napoca, Romania.
\item   \textbf{R. D.  G\u{a}ceanu}, H. F. Pop, An Incremental ASM-based Fuzzy Clustering Algorithm, Informatics'2011, Slovakia, i'11:Proceedings of the Eleventh International Conference on Informatics, Informatics 2011, Eds: V. Novitzk\'{a}, \u{S}tefan Hud\'{a}k, November 16--18, pp. 198--204, Ro\u{z}\u{n}ava, Slovakia.
\item  I. G. Czibula, G. Czibula, \textbf{R. D. G\u{a}ceanu}, Intelligent Data Structures Selection Using Neural Networks, Knowledge and Information Systems, Springer London, pages 1--22, 
10.1007/s10115-011-0468-3.
\item  G. Czibula, I. G. Czibula, \textbf{R. D. G\u{a}ceanu}, A Support Vector Machine Model For Intelligent Selection of Data Representations, Applied Soft Computing --- under review.

\end{itemize}

\end{comment}
