\documentclass{report}

\usepackage{dirtytalk}

\begin{document}
\centerline{\sc \large Answer to reviewers}
\vspace{2.5pc}
\say{This paper presents a hardware implementation of a wirelessly controlled thermostat. It gives a very short
introduction, then it follows with a description of the hardware used in the implementation and gives some
indication that the thermostat works. The main contribution of the paper is in describing the hardware used;
the fuzzy logic should merit more attention from the author.} \par
More details about fuzzy logic and our approach to it were added, as suggested, in sections
\textbf{Introduction} and \textbf{Thermostat fuzzy engine}. \par \vspace{.7pc}

\say{Also, the author does not relate to the wireless thermostats that exist on the market.} \par
A new section was added, \textbf{Related work}, that presents the currently available thermostats on the market.
\par \vspace{.7pc}

\say{The introduction is weak, it does not clearly state what is the scope of this paper and it does not
position the work done here in the current literature.} \par
Added more details about works on fuzzy logic in the context of temperature control in section
\textbf{Introduction}. \par \vspace{.7pc}

\say{Figure 1 from section 3 is not introduced in the text.}
Figure 1 is now introduced in the text just after Definition 1.  \par \vspace{.7pc}

\say{Equation (2) is incorrect?} \par
The problematic equation was corrected. \par \vspace{.7pc}

\say{Figure 2 is not related to the example given in section III definition 4.} \par
Figure 2 was removed from the text. \par \vspace{.7pc}

\say{Figure 3 is not explained in the text.} \par
Now Figure 2, is explained at the end of subsection \textbf{Fuzzy logic reasoning}. \par \vspace{.7pc}

\say{After reading the introduction one has the expectation that section III gives an introduction to the
state of art of the Internet of Things, but this is not the case. Section III gives a simple introduction to
fuzzy logic.} \par
A new section was introduced under \textbf{Theoretical background} that introduces the reader to the Internet
of Things.  \par \vspace{.7pc}

\say{In section V you state \say{Even with extreme differences, the values drop back to normal in a fair amount of
time.}. What do you mean by \say{normal} and \say{a fair amount of time}?}
Rephrased the statement to eliminate ambiguities. \par \vspace{.7pc}

\say{Please give more experimental result.} \par
Added more experimental results in section \say{Results and discussions}.  \par \vspace{.7pc}

\say{PLease cite the work that is not yours} \par
Added citations to work not created by the author. \par \vspace{.7pc}

Some typos: \par
\say{paragraph 1: possiblities -\textgreater possibilities, house-hold -\textgreater household} \par
\say{paragraph 2: materials, arts, and subassemblies -\textgreater parts?;} \par
\say{of commerce and culture. [1] -\textgreater of commerce and culture [1].} \par
\say{paragraph 3: contex lead to -\textgreater context leads...} \par
\say{paragraph 4: described by this paper -\textgreater described in...;} \par
\say{An in depth description -\textgreater An in-depth... } \par
\say{human kind -\textgreater humankind} \par
\say{Fuzzy logic is build -\textgreater Fuzzy logic is built} \par
\say{which makes it possible -\textgreater that makes it possible} \par
\say{another application processor.[5] -\textgreater another application processor [5].} \par
\say{Atmel Attiny85 (Figure 5). [8] -\textgreater Atmel Attiny85 (Figure 5) [8].} \par
The above language issues are now fixed. \par \vspace{.7pc}

Phrasing problems: \par
\say{paragraph 5: please rephrase "Section III presents information relevant
for the understanding of the chapter that follows"} \par
\say{please rephrase the statement \say{The Internet of Things enables the world
to research itself and find patterns that were otherwise invisible, thus
leading to a greater understanding of the context we are living in, which in
turn lets us control that context in a more efficient manner.}} \par
\say{In the rest of the chapter, the concepts surrounding fuzzy logic will be
explained. -\textgreater Next, the (this is a section not a chapter)}
\say{please rephrase paragraph 6 \say{Since its release...}} \par
Rephrased all of the above statements.\par \vspace{.7pc}

Structure observations: \par
\say{paragraph 4: I think this statement is redundant \say{An in depth description of the architecture will be
presented in section IV.}, you already state this in paragraph 5.} \par
Removed mentioned statement.  \par \vspace{.4pc}

\say{You say \say{For the application in discussion, this fact enables one to monitor and control one’s house
temperature setting from anywhere thus increasing the comfort level.} but you haven't stated what the
application is yet.} \par
\textbf{Introduction} now has short description of the application.
\end{document}
